Visualizing probability distributions across bivariate cyclic temporal granularities

### 2021-05-10 reviews/response.Rmd

A3. Aperiodic linear granularities are those that can not be defined by Definition 6. If $M_i$ is periodic, then $M = \bigcup M_i$ is periodic, but if each $M_i$'s are aperiodic, then $M$ could be periodic or aperiodic. In Definition 10, we want $M$ to be aperiodic. Definition 10 and introduction of Section 3.3 briefly rephrased to improve clarity.

Q4. $w$ in $T_w$ is not well defined for circular granularities in Section 3.2 & 3.5. The definition of $T_w$ uses $T_w$ itself in the formula making it hard to understand. Relevantly, what is the interpretation of $k$ where $w = 0, 1, \dots k-1$? In my opinion, the number of cycles
should be defined for cyclic granularities, for example, $w_{B,G}(z) = \lfloor z/P(B;G) \rfloor$, which
represent the cycle that the granule is in.

A4. Definition of $w$ and $R'$ included in Definition 9.

$T_w$ are the sets of indices of $B$ such that $G'(w) = \bigcup_{z \in T_w}B(z)$. For example, if $B$ is `day` and $G'$ is `month`, then $G'(0) = {B(0)\cup B(1)\cup \dots \cup B(30)}$, $G'(1) = {B(31)\cup B(32)\cup \dots \cup B(58)}$ corresponding to January and February. Then $T_0 = \{0, 1, 2, \dots, 30\}$ and $T_1 = \{31, 32, \dots, 58\}$. If $z$ belongs to $k^{th}$ granule of $G'$, then $z \in T_k$. For example, if $z = 31$ then $z \in T_1$ and thus $k = 1$.

@@

## Places that need clarification

Q1. Page 7, Definition 6. Is "the number of granules of H" finite or infinite? If each granule $G(i)$ has the index $i \in Z_{>=0}$, then the phrase is similar as "the number of non-negative integers."

A1. Number of granules of $H$ should be finite. Definition rephrased to account for that.

Q2. Page 7, Lines 19-20. It is claimed that quasi-periodic relationship has a finite number of periods where granularities behave in an anomalous way. What does the finite number of periods mean and why is it finite? Does it mean a finite number of granularity groupings? Does it mean a finite number of irregular cycles? By Definition 4 of Bettini & De Sibi (2000), $E_1, \dots, E_z$ are the granularity exceptions, but the number of granularity exceptions does not have to be finite.

A2. "Number of periods" rephrased as "spans of time". Bettini & De Sibi (2000) states in P57 L17 while introducing quasi-periodic relationships that "except for a finite number of spans of time where they behave in an anomalous way".

@@

Q2. Page 6, what is the difference between finer than and group into in Definitions 4 and 5? On Page 7, Line 34, they are used as alternative choices. Can you give an example
that $G \preceq H$ does not imply $G  \trianglelefteq H$, or vice versa? "finer than" is not used a lot in this paper. If the two concepts are similar, why not pick one of them?

A2. If $G \trianglelefteq H$, then every granule of $H$ can be expressed as an union of some set of granules in $G$. If $G \preceq H$, then every granule of $G$ is a subset of some granule of $H$. These are not equivalent. Examples added in the paper after their definition in Page 6.

Q3. Page 16, Line 13, multiple order-up quasi-circular granularities. The equations for this
operation are not trivial to be ignored. Should be added if possible.

A3. Equations (5) and (6) are used for this operation (with sides interchanged) and hence are not added again.

### 2021-05-10 main.Rmd
made graph label consistent and deleted word plot

(ref:allFig) Distribution of energy consumption displayed through letter value plots used to illustrate harmonies and clashes: (a) across month-of-year faceted by quarter-of-year; (b) across weekday/weekend faceted by quarter-of-year; (c) across quarter-of-year faceted by weekday/weekend. (a) shows a clash since there are empty combinations. (b) and (c) show harmonies since each quarter include both weekdays and weekends. It can be seen in (b) that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter.
For example, the letter value D for weekdays mostly corresponds to letter value E for weekends, implying there are lower values of energy consumption during weekdays in the second quarter. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). (c) switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, the lower D and E letter values are most different across different quarters for weekdays and weekends respectively.
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->

@@

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. Plot **a** shows granularity 2 faceted by granularity 1; plots **b** and **c** shows the reverse mapping. Plot **a** allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. Plots **b** and **c** examine the temporal trend of consumption over the course of a day, separately for the type of day. Plot **b** uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. Plot **c** uses a violin plot emphasizes subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.

@@

(ref:cricex) Runs per over shown with different distribution displays, and granularities. Plot **a** shows letter value plots across overs faceted by innings. For the team batting in the first innings, there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. Plot **b** shows quantile plots of runs per over across an indicator of wickets in the previous over faceted by current over. This indicates that at least one wicket in the previous over leads to a lower median run rate and quartile spread in the subsequent over, regardless of the over of the innings.

>>>>

(ref:allFig) Distribution of energy consumption displayed through letter value plots used to illustrate harmonies and clashes: **a** across month-of-year faceted by quarter-of-year; **b** across weekday/weekend faceted by quarter-of-year; **c** across quarter-of-year faceted by weekday/weekend. **a** shows a clash since there are empty combinations. **b** and **c** show harmonies since each quarter include both weekdays and weekends. It can be seen in **b** that for every quarter (mapped to facet), weekend and weekday consumption are fairly similar except for the second quarter.
For example, the letter value D for weekdays mostly corresponds to letter value E for weekends, implying there are lower values of energy consumption during weekdays in the second quarter. This is probably because of lower temperatures in the second quarter compared to the first quarter (summer in Australia). **c** switches the granularities mapped to the x-axis and the facets and helps to compare quarters within weekdays and weekends. For example, the lower D and E letter values are most different across different quarters for weekdays and weekends respectively.
<!-- For example, for weekdays the interquartile range of consumption reduces over the year, whereas this pattern is not true for weekends. -->

@@

(ref:bothcust) Energy consumption of a single customer shown with different distribution displays, and granularity arrangements. Two granularities are used: 1. hour of the day; and 2. weekday/weekend. **a** shows granularity 2 faceted by granularity 1; **b** and **c** shows the reverse mapping. **a** allows comparison of usage by workday within each hour of the day using side-by-side boxplots, showing that on work days there is more consumption early in the day. **b** and **c** examine the temporal trend of consumption over the course of a day, separately for the type of day.**b** uses an area quantile to emphasize the time component; e.g., median consumption shows prolonged high usage in the morning on weekdays. **c** uses a violin plot emphasizes subtler distributional differences across hours, showing that morning use on weekdays is bimodal, and on some work days there is low usage possibly indicating the person is working from home or having a late start.

@@

(ref:cricex) Distributions of runs per over shown with different distribution displays, and granularities. **a** shows letter value plots across overs faceted by innings. For the team batting in the first innings, there is an upward trend of runs per over, while there is no such pattern of runs for the teams batting in the second innings. **b** shows quantile plots of runs per over across an indicator of wickets in the previous over faceted by current over. This indicates that at least one wicket in the previous over leads to a lower median run rate and quartile spread in the subsequent over, regardless of the over of the innings.
